Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words

### 2020-06-24 paper/supplementary_material.Rmd
presubmission clean up

---
title: "How young children integrate information during word learning"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

[Next](#cognitive-models), we introduce a computational cognitive model (**integration model**) in which we formalize the process of how information sources are integrated. As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.

In the [final section](#explanation), we turn to the process by which information is integrated. We contrast the process of Bayesian inference we introduced in our model with a biased integration process in which some inforamtion sources are weighted as more important. As part of this, we also explore alternative ways to think about developmental change in the integration process.

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were $\mathcal{N}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.

The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect. Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights. The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred. WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data. The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)). Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept (i.e. mutual exclusivity inference at age 2.00). The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the strength of the mutual exclusivity inference depended on age as well as the familiar object.

@@

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction. Combining the two procedures created two alignment conditions: In the *congruent condition*, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. In this case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different information sources. We investigate this question in depth in the [modelling](#cognitive-models) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

@@

The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age. To do so, we use Bayesian cognitive models of pragmatic reasoning. We first describe an **integration model** which we think best represents the inference and integration processes and then specify how this model captures developmental change. Next, we ask how well this model *predicts* how children integrate information. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particular familiar object) as well as the common ground inference, what can we say about what happens when they are combined. We then test the predictive power of the model by comparing the model predictions to the data from Experiment 3. We use formal model comparison methods to test the **integration model** against a range of alternative models.

@@

The informativity of each utterance is given by imagining which referent a literal listener ($L_0$), who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar vs. unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete ignorance, corresponding to maximal uncertainty about which object the word applies to. 
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

@@

Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance, before actually hearing the utterance. In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance (see \@ref(fig:fig1)B). Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusitivity are cues to different referents (see Figure \@ref(fig:fig1)C).  
We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [@akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.

```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **integration model** used for *Explanation*. $RSA$ represents the general model architecture and paremeters defined by Eq. \\@ref(eq:rsabasic1) - \\@ref(eq:rsabasic3). $L_1$ represents the RSA model defined by Eq. \\@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt. 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$. This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age). Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt. 1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt. 2).  Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively). Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $\\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\ 
$P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
$P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})$
};

@@

In this section we evaluate different models in terms of how well they *predict* information integration. That is, in a situation in which we know the development of the (object specific) mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3). Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating mixture model, described below). To generate *a priori* predictions, we independently estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.

@@

To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150,000 samples from each chain and removing the first 50,000 for burn-in. We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains. To direclty access the model predictions see the file `model_comparison.Rmd` in the online repository.

Next, we combined the parameters according to the four models described below. Note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in terms of which parameters they included. The models described below are a full model (**integration model**) and three lesioned models, which selectively omit one type of information. The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated. All models used age-specific parameters when the parameter was present. We do not compare models that make different assumptions about how information is integrated, since they require additional parameters specific to Experiment 3. We consider the question of alternative integration models in the [explanation](#explanation) section.

@@

#### Integration model

The **integration model** serves as the full model and takes in all available information. That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above. Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from Experiment 3.

We compare this model to three alternative, "lesioned" models that lack certain components of the full integration model.

```{r fig5, include = T, cache = T, fig.cap = "Predicting information integration across development. Model predictions based on the integration model. Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution. Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition. Familiar objects are ordered based on their rated age of acquisition (left to right). Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey). Light dots are individual data points.", fig.width=12, fig.height = 4}
# comb_data_binned <- comb_data%>%
#   group_by(subage, alignment, item)%>%
#   summarize(k = sum(correct), n = n())%>%
#   ungroup() %>%
#   mutate(a = 1 + k,
#          b = 1 + n - k,
#          data_mean = (a-1)/(a+b-2),
#          data_ci_lower  = qbeta(.025, a, b),
#          data_ci_upper = qbeta(.975, a, b),
#          age = factor(subage))%>%
#   select(-a,-b,-n,-k)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# select_pred <- sample(1:20000, 60)
# 
# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
#   filter(iteration %in% select_pred)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# 
#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")

@@

A marginally less-complex model than the full integration model uses the same model architecture, taking in speaker informativeness and common ground sensitivity, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model. In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects). The **no word knowledge model** takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation. Formally, the semantic knowledge for each item is the same: $\theta_{i} = \mu^\theta_0 +  i \cdot \mu^\theta_1$. That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.

@@

We compared the models mentioned above in two ways. First, we used correlations between model predictions and the data. For this analysis, we binned the model predictions and the data by age in years and by the type of familiar object. Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models. The results shows a very high correlation between the predictions of the **integration model** and the data in all age groups indicating that the model accurately captures the variation in the data. Correlations for the **integration model** were also higher compared to the other models considered. The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds. The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions in the congruent condition. This results from the fact that 4-year-olds show very high performance both the mututal exclusivity and common ground tasks. When combined in the model, the two inferences amplify one another because we assume no cost of integration. We maintain no cost to integration because positing integration cost introduces a free parameter that could only be estimated based on the integration data of Experiment 3 itself (i.e., such a model would not make precise *a priori* predictions).

We additionally compared models based on the marginal likelihood of the data under each model -- the likelihood of the data averaging over ("marginalizing over") the prior distribution on parameters; the pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor (see file `model_comparison.Rmd` in the associated online repository). Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by the prior probabilities of those parameter values); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the potential gains in predictive accuracy that a model with more parameters can achieve [@lee2014bayesian]. For this analysis, we treated age continuously. Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons. The results show that the **integration model**, by far, outperformed all the other models. When comparing the lesioned models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the **no mutual exclusivity model**.

Taken together, these analyses showed two things. First, the **integration model** makes accurate predictions about how mutual exclusivity and common ground inferences are integrated. It does so based on knowing the strength and development of each inference alone, and incorporating them into a structured probabilistic model of pragmatic reasoning. Second, models that omit one or more types of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make appreciably worse predictions. This result exemplifies that children across the entire age range flexibly integrate all the available information. In the next section we ask investigate alternative formulations of the process of information integration.

@@

In this section we explore how to best explain information integration across development. We explore alternative ways to think about information integration. The **integration model** outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference. In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.

Information sources need not be integrated in a Bayesian manner as part of the same pragmatic reasoning architecture. Instead, the common ground and mutual exclusitivity inferences we consider could be computed separately and combined in a more heuristic fashion. A listener could integrate these two independent inferences in an additive manner, weighting the sources of information by some ratio $\phi$. $\phi$ is then a bias to prefer one type of inference relative to the other. We formalize this alternative hypothesis as a  **mixture model**.

The **integration** and **mixture** models have potentially different implications for developmental change.
The **integration model** assumes that the process by which information is integrated remains constant across development. What changes is children's sensitivity to different cues: semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground. The **mixture model** alternatively posits that there is some bias or preference for one information source, and this bias could change across development. This **developmental mixture model**  makes the same assumptions about developmental change in sensitivities to individual information sources as the **integration model** but, in addition, assumes that the way that the mutual exclusivity and the common ground inference are combined changes over time. This model is structurally identical to the **mixture model** but the mixture parameter $\phi$ is a function of age, which we model via a logistic-linear model: $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$, whose parameters we infer via Bayesian inference.

>>>>

---
title: "Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

[Next](#cognitive-models), we introduce a computational cognitive model (**rational integration model**) in which we formalize the process of how information sources are integrated. As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the modeling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.

In the [final section](#explanation), we turn to the process by which information is integrated. We contrast the process of Bayesian inference we introduced in our model with a biased integration process in which some information sources are weighted as more important. As part of this, we also explore alternative ways to think about developmental change in the integration process.

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were $\mathcal{N}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospectively included it to be consistent with Experiment 2 and 3.

The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. To assess the variability across objects, we compared the fit of the above model to a model lacking `object` as a random effect. Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights. The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred. WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data. The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)). Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept (i.e. mutual exclusivity inference at age 2.00). The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the strength of the mutual exclusivity inference depended on age as well as the familiar object.

@@

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licenses but also the role that each object (novel and familiar) had played in the preceding interaction. Combining the two procedures created two alignment conditions: In the *congruent condition*, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. In this case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different information sources. We investigate this question in depth in the [modelling](#cognitive-models) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

@@

The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age. To do so, we use Bayesian cognitive models of pragmatic reasoning. We first describe an **rational integration model** which we think best represents the inference and integration processes and then specify how this model captures developmental change. Next, we ask how well this model *predicts* how children integrate information. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particular familiar object) as well as the common ground inference, what can we say about what happens when they are combined. We then test the predictive power of the model by comparing the model predictions to the data from Experiment 3. We use formal model comparison methods to test the **rational integration model** against a range of alternative models.

@@

The informativity of each utterance is given by imagining which referent a literal listener ($L_0$), who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ corresponds to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar vs. unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete ignorance, corresponding to maximal uncertainty about which object the word applies to. 
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

@@

Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance, before actually hearing the utterance. In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance (see \@ref(fig:fig1)B). Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusivity are cues to different referents (see Figure \@ref(fig:fig1)C).  
We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [@akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.

```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **rational integration model** used for *Explanation*. $RSA$ represents the general model architecture and paremeters defined by Eq. \\@ref(eq:rsabasic1) - \\@ref(eq:rsabasic3). $L_1$ represents the RSA model defined by Eq. \\@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt. 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$. This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age). Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt. 1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt. 2).  Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively). Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $\\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Rational integration model\\ $P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\ 
$P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
$P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})$
};

@@

In this section we evaluate different models in terms of how well they *predict* information integration. That is, in a situation in which we know the development of the (object specific) mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3). Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating biased model, described below). To generate *a priori* predictions, we independently estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.

@@

To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150,000 samples from each chain and removing the first 50,000 for burn-in. We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains. To directly access the model predictions see the file `model_comparison.Rmd` in the online repository.

Next, we combined the parameters according to the four models described below. Note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in terms of which parameters they included. The models described below are a full model (**rational integration model**) and three lesioned models, which selectively omit one type of information. The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated. All models used age-specific parameters when the parameter was present. We do not compare models that make different assumptions about how information is integrated, since they require additional parameters specific to Experiment 3. We consider the question of alternative integration models in the [explanation](#explanation) section.

@@

#### Rational integration model

The **rational integration model** serves as the full model and takes in all available information. That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above. Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from Experiment 3.

We compare this model to three alternative, "lesioned" models that lack certain components of the rational integration model.

```{r fig5, include = T, cache = T, fig.cap = "Predicting information integration across development. Model predictions based on the rational integration model. Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution. Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition. Familiar objects are ordered based on their rated age of acquisition (left to right). Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey). Light dots are individual data points.", fig.width=12, fig.height = 4}
# comb_data_binned <- comb_data%>%
#   group_by(subage, alignment, item)%>%
#   summarize(k = sum(correct), n = n())%>%
#   ungroup() %>%
#   mutate(a = 1 + k,
#          b = 1 + n - k,
#          data_mean = (a-1)/(a+b-2),
#          data_ci_lower  = qbeta(.025, a, b),
#          data_ci_upper = qbeta(.975, a, b),
#          age = factor(subage))%>%
#   select(-a,-b,-n,-k)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# select_pred <- sample(1:20000, 60)
# 
# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
#   filter(iteration %in% select_pred)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# 
#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")

@@

A marginally less-complex model than the rational integration model uses the same model architecture, taking in speaker informativeness and common ground sensitivity, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model. In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects). The **no word knowledge model** takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation. Formally, the semantic knowledge for each item is the same: $\theta_{i} = \mu^\theta_0 +  i \cdot \mu^\theta_1$. That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.

@@

We compared the models mentioned above in two ways. First, we used correlations between model predictions and the data. For this analysis, we binned the model predictions and the data by age in years and by the type of familiar object. Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models. The results shows a very high correlation between the predictions of the **rational integration model** and the data in all age groups indicating that the model accurately captures the variation in the data. Correlations for the **rational integration model** were also higher compared to the other models considered. The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds. The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions in the congruent condition. This results from the fact that 4-year-olds show very high performance both the mutual exclusivity and common ground tasks. When combined in the model, the two inferences amplify one another because we assume no cost of integration. We maintain no cost to integration because positing integration cost introduces a free parameter that could only be estimated based on the integration data of Experiment 3 itself (i.e., such a model would not make precise *a priori* predictions).

We additionally compared models based on the marginal likelihood of the data under each model -- the likelihood of the data averaging over ("marginalizing over") the prior distribution on parameters; the pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor (see file `model_comparison.Rmd` in the associated online repository). Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by the prior probabilities of those parameter values); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the potential gains in predictive accuracy that a model with more parameters can achieve [@lee2014bayesian]. For this analysis, we treated age continuously. Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons. The results show that the **rational integration model**, by far, outperformed all the other models. When comparing the lesioned models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the **no mutual exclusivity model**.

Taken together, these analyses showed two things. First, the **rational integration model** makes accurate predictions about how mutual exclusivity and common ground inferences are integrated. It does so based on knowing the strength and development of each inference alone, and incorporating them into a structured probabilistic model of pragmatic reasoning. Second, models that omit one or more types of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make appreciably worse predictions. This result exemplifies that children across the entire age range flexibly integrate all the available information. In the next section we ask investigate alternative formulations of the process of information integration.

@@

In this section we explore how to best explain information integration across development. We explore alternative ways to think about information integration. The **rational integration model** outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference. In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.

Information sources need not be integrated in a Bayesian manner as part of the same pragmatic reasoning architecture. Instead, the common ground and mutual exclusivity inferences we consider could be computed separately and combined in a more heuristic fashion. A listener could integrate these two independent inferences in an additive manner, weighting the sources of information by some ratio $\phi$. $\phi$ is then a bias to prefer one type of inference relative to the other. We formalize this alternative hypothesis as a **biased model**.

The **rational integration** and **biased integration** models have potentially different implications for developmental change.
The **rational integration model** assumes that the process by which information is integrated remains constant across development. What changes is children's sensitivity to different cues: semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground. The **biased integration model** alternatively posits that there is some bias or preference for one information source, and this bias could change across development. This **developmental bias model**  makes the same assumptions about developmental change in sensitivities to individual information sources as the **rational integration model** but, in addition, assumes that the way that the mutual exclusivity and the common ground inference are combined changes over time. This model is structurally identical to the **biased model** but the bias parameter $\phi$ is a function of age, which we model via a logistic-linear model: $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$, whose parameters we infer via Bayesian inference.

In this section, we make use of all the available data to arbitrate between these alternative models (a fully Bayesian analysis). As before, Experiments 1 and 2 directly constrain the parameters governing semantic knowledge, speaker informativeness, and the prior distribution over referents (via common ground; Expt. 2). Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the bias parameter for the **biased models** (see Figure \@ref(fig:bda)).
